---
title: "ghana_project"
author: "Zixin"
date: "`r format(Sys.Date(), '%d/%m/%y')`"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(haven)
library(dplyr)
library(readxl)
library(ggplot2)
library(scales)
library(pander)
library(reshape2)
library(sandwich)
library(stargazer)
library(tidyverse)
library(jtools)
```


```{r echo=T, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
ACE_G <- read_dta("ghana_data/ACE_G.dta")
data1 <- read_dta("ghana_data/ACE_G.dta", col_select = c(hid,b22i,b22ii,b22iii,b22iv,b22_a,b22b_1,b22b_2,b22b_3,b24a,b24b,b24c_1,b24c_2,b24c_3,b24c_4,b24d_1,b24d_2,b24d_3,b24d_4, b14e_1, b14e_2,c7c, c4,c5, c7a, c7b, c7c, c9a,c9b,c9c,c9d,c11a,c11b,c11c))

```

## Description
### b22. Do you currently sell to any of the following groups? {.tabset}
#### Government
```{r r Plot 1.1, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = data1, aes(x= b22i)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Do you currently sell to the government?") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(breaks = seq(0,650,50)) +
  theme_light() 
x
```

#### End-customer
```{r r Plot 1.2, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = data1, aes(x= b22ii)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Do you currently sell to the end-customer?") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(breaks = seq(0,650,50)) +
  theme_light() 
x
```

#### Another business or distributer, selling directly to the end-customer
```{r r Plot 1.3, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = data1, aes(x= b22iii)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Do you currently sell to the another business or distributer, selling directly to the end-customer?") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(breaks = seq(0,650,50)) +
  theme_light() 
x
```

#### A buyer not selling to the end-customer, as the production chain is longer
```{r r Plot 1.4, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = data1, aes(x= b22iv)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Do you currently sell to a buyer not selling to the end-customer, as the production chain is longer") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(breaks = seq(0,650,50)) +
  theme_light() 
x
```


### How many buyers do you have?
```{r r Plot 2.1, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = data1, aes(x= b22_a)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("How many buyers do you have?") +
  scale_x_continuous(breaks=seq(1,3,1), labels = c("1 buyer", "2-5 buyers", "More than 5 buyers")) +
  scale_y_continuous(breaks = seq(0,650,50)) +
  theme_light() 
x
```

### Where are they located?   {.tabset}
```{r}
sample1 <- subset(data1, select = c(hid,b22_a,b22b_1,b22b_2,b22b_3, b14e_1,b14e_2,c7c))
#sample1 <- subset(data1, is.na(data1$b22b_1)==FALSE)
# make 123 become 1, because they all mean yes
sample1_clean <- sample1 %>%
  mutate(district = b22b_1,
         within_ghana = ifelse(b22b_2==2, 1, b22b_2),
         outside_ghana = ifelse(b22b_3==3, 1, b22b_3)) %>%
  select(!c(b22b_1,b22b_2,b22b_3))
## combine district and within_ghana into one column
sample1_merge <- sample1_clean %>%
  mutate(district_or_within_ghana = ifelse(is.na(district), within_ghana, district)) %>%
  select(!c(district,within_ghana))
```

#### only outside Ghana
```{r r Plot 2.2, results='asis', message=FALSE, warning=FALSE}
sample_outside_only <- subset(sample1_merge, is.na(district_or_within_ghana) == TRUE & outside_ghana == 1)
x <- ggplot(data = sample_outside_only, aes(x= b22_a)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("The distribution of selling only to outside Ghana") +
  scale_x_continuous(breaks=seq(1,3,1), labels = c("1 buyer", "2-5 buyers", "More than 5 buyers")) +
  scale_y_continuous(limits = c(0,475), breaks = seq(0, 475, by = 25)) +
  theme_light() 
x
#table(sample_outside_only$b22_a)
```

The distribution of the number of female
```{r}
#table(sample_outside_only$b14e_1)
pander(summary(sample_outside_only$b14e_1))
```
The distribution of the number of male
```{r}
#table(sample_outside_only$b14e_2)
pander(summary(sample_outside_only$b14e_2))
```
The distribution of estimated sales in 2019
```{r}
#table(sample_outside_only$c7c)
pander(summary(sample_outside_only$c7c))
```


#### only district
```{r r Plot 2.3, results='asis', message=FALSE, warning=FALSE}
sample_district <- subset(sample1_clean, is.na(outside_ghana) == TRUE & is.na(within_ghana) == TRUE & district == 1)
x <- ggplot(data = sample_district, aes(x= b22_a)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("The distribution of selling only to district") +
  scale_x_continuous(breaks=seq(1,3,1), labels = c("1 buyer", "2-5 buyers", "More than 5 buyers")) +
  scale_y_continuous(limits = c(0,475), breaks = seq(0, 475, by = 25)) +
  theme_light() 
x
#table(sample_district$b22_a)
```
The distribution of the number of female
```{r}
#table(sample_district$b14e_1)
pander(summary(sample_district$b14e_1))
```
The distribution of the number of male
```{r}
#table(sample_district$b14e_2)
pander(summary(sample_district$b14e_2))
```
The distribution of estimated sales in 2019
```{r}
#table(sample_district$c7c)
pander(summary(sample_district$c7c))
```

#### district and within Ghana
```{r r Plot 2.5, results='asis', message=FALSE, warning=FALSE}
sample_within <- subset(sample1_merge, is.na(outside_ghana) == TRUE & district_or_within_ghana == 1)
x <- ggplot(data = sample_within, aes(x= b22_a)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("The distribution of selling only to district or within Ghana") +
  scale_x_continuous(breaks=seq(1,3,1), labels = c("1 buyer", "2-5 buyers", "More than 5 buyers")) +
  scale_y_continuous(limits = c(0,475), breaks = seq(0, 475, by = 25)) +
  theme_light() 
x
#table(sample_within$b22_a)
```

The distribution of the number of female
```{r}
#table(sample_within$b14e_1)
pander(summary(sample_within$b14e_1))
```
The distribution of the number of male
```{r}
#table(sample_within$b14e_2)
pander(summary(sample_within$b14e_2))
```
The distribution of estimated sales in 2019
```{r}
#table(sample_within$c7c)
pander(summary(sample_within$c7c))
```

#### both to district_or_within and outside Ghana
```{r r Plot 2.6, results='asis', message=FALSE, warning=FALSE}
sample_both <- subset(sample1_merge, is.na(outside_ghana) == FALSE & is.na(district_or_within_ghana) == FALSE)
x <- ggplot(data = sample_both, aes(x= b22_a)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("The distribution of selling both to district_or_within Ghana and outside Ghana") +
  scale_x_continuous(breaks=seq(2,3,1), labels = c("2-5 buyers", "More than 5 buyers")) +
  scale_y_continuous(limits = c(0,475), breaks = seq(0, 475, by = 25)) +
  theme_light() 
x
#table(sample_both$b22_a)
```
The distribution of the number of female
```{r}
#table(sample_both$b14e_1)
pander(summary(sample_both$b14e_1))
```
The distribution of the number of male
```{r}
#table(sample_both$b14e_2)
pander(summary(sample_both$b14e_2))
```
The distribution of estimated sales in 2019
```{r}
#table(sample_both$c7c)
pander(summary(sample_both$c7c))
```

### b24.  I sell my product to……… {.tabset}
```{r}
sample_b24 <- subset(data1, 
                     select=c(hid,b24a,b24b,b24c_1,b24c_2,b24c_3,b24c_4,
                              b24d_1,b24d_2,b24d_3,b24d_4)) %>%
              mutate(end_customer = ifelse(is.na(b24a)==TRUE, 2, 1),
                     further_customer = ifelse(is.na(b24b)==TRUE, 2, 1),
                     end_district = ifelse(is.na(b24c_1)==TRUE, 2, 1),
                     end_within_ghana = ifelse(is.na(b24c_2)==TRUE, 2, 1),
                     end_outside_ghana = ifelse(is.na(b24c_3)==TRUE, 2, 1),
                     further_district = ifelse(is.na(b24d_1)==TRUE, 2, 1),
                     further_within_ghana = ifelse(is.na(b24d_2)==TRUE, 2, 1),
                     further_outside_ghana = ifelse(is.na(b24d_3)==TRUE, 2, 1))
```

#### End-customer (s)
```{r r Plot 3.1, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = sample_b24, aes(x= end_customer)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("I sell my product to End-customer (s)") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(limits = c(0,600), breaks = seq(0, 600, by = 50)) +
  theme_light() 
x
```

##### Where are they located? {.tabset}
###### only district
```{r r Plot 3.1.1, results='asis', message=FALSE, warning=FALSE}
b24_district_only <- subset(sample_b24, end_outside_ghana == 2 & end_within_ghana == 2)
x <- ggplot(data = b24_district_only, aes(x= end_district)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("End-customer (s) are located only in your district.") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(limits = c(0,280),breaks = seq(0, 280, by = 20)) +
  theme_light() 
x
```

###### district and within Ghana
```{r r Plot 3.1.2, results='asis', message=FALSE, warning=FALSE}
b24_within <- subset(sample_b24, end_outside_ghana == 2 & end_district == 1)
x <- ggplot(data = b24_within, aes(x= end_within_ghana)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("End-customer (s) are located in both your district and another district within Ghana.") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(limits = c(0,280), breaks = seq(0, 280, by = 20)) +
  theme_light() 
x
```

###### only outside Ghana
```{r r Plot 3.1.3, results='asis', message=FALSE, warning=FALSE}
b24_outside_only <- subset(sample_b24, end_district == 2 & end_within_ghana == 2)
x <- ggplot(data = b24_outside_only, aes(x= end_outside_ghana)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("End-customer (s) are located only outside Ghana.") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(limits = c(0,280), breaks = seq(0, 280, by = 20)) +
  theme_light() 
x
```

###### both to district_or_within and outside Ghana
```{r r Plot 3.1.4, results='asis', message=FALSE, warning=FALSE}
b24_both <- subset(sample_b24, end_district == 1 & end_within_ghana == 1)
x <- ggplot(data = b24_both, aes(x= end_outside_ghana)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("End-customer (s) are located both to district_or_within and outside Ghana.") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(limits = c(0,280), breaks = seq(0, 280, by = 20)) +
  theme_light() 
x
```

#### Buyer(s) who sells to further customer
```{r r Plot 3.2, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = sample_b24, aes(x= further_customer)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("I sell my product to Buyer(s) who sells to further customer") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(limits = c(0,600), breaks = seq(0, 600, by = 50)) +
  theme_light() 
x
```

##### Where are they located? {.tabset}
###### only district
```{r r Plot 3.2.1, results='asis', message=FALSE, warning=FALSE}
b24_district_only_f <- subset(sample_b24, further_outside_ghana == 2 & further_within_ghana == 2)
x <- ggplot(data = b24_district_only_f, aes(x= further_district)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Buyers with further customers are located only in your district.") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(limits = c(0,400),breaks = seq(0, 400, by = 20)) +
  theme_light() 
x
```

###### district and within Ghana
```{r r Plot 3.2.2, results='asis', message=FALSE, warning=FALSE}
b24_within_f <- subset(sample_b24, further_outside_ghana == 2 & further_district == 1)
x <- ggplot(data = b24_within_f, aes(x= further_within_ghana)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Buyers with further customers are located in both your district and another district within Ghana.") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(limits = c(0,400), breaks = seq(0, 400, by = 20)) +
  theme_light() 
x
```

###### only outside Ghana
```{r r Plot 3.2.3, results='asis', message=FALSE, warning=FALSE}
b24_outside_only_f <- subset(sample_b24, further_district == 2 & further_within_ghana == 2)
x <- ggplot(data = b24_outside_only_f, aes(x= further_outside_ghana)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Buyers with further customers are located only outside Ghana.") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(limits = c(0,400), breaks = seq(0, 400, by = 20)) +
  theme_light() 
x
```

###### both to district_or_within and outside Ghana
```{r r Plot 3.2.4, results='asis', message=FALSE, warning=FALSE}
b24_both_f <- subset(sample_b24, further_district == 1 & further_within_ghana == 1)
x <- ggplot(data = b24_both_f, aes(x= further_outside_ghana)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Buyers with further customers are located both to district_or_within and outside Ghana.") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(limits = c(0,400), breaks = seq(0, 400, by = 20)) +
  theme_light() 
x
```

### c4: Profit
#### before covid-19
```{r}
pander(summary(data1$c4))
```

#### after covid-19
```{r}
pander(summary(data1$c5))
```

### c7: What estimated sales (in GHC) did this business make in
#### 2020
```{r}
pander(summary(data1$c7a))
```

#### 2019
```{r}
pander(summary(data1$c7b))
```

#### 2018
```{r}
pander(summary(data1$c7c))
```

### c9: Beyond Ghana, in which markets did YOU sell? {.tabset}
```{r}
sample_market <- subset(data1, is.na(b22b_3) == FALSE, select = c(hid,b22b_3,c9a, c9b, c9c,c9d)) %>%
                  mutate(market_1 = ifelse(is.na(c9a)==TRUE, 0, c9a),
                         market_2 = ifelse(is.na(c9b)==TRUE, 0, c9b),
                         market_3 = ifelse(is.na(c9c)==TRUE, 0, c9c),
                         market_4 = ifelse(is.na(c9d)==TRUE, 0, c9d))
```
#### 1
```{r r Plot 4.1.1, results='asis', message=FALSE, warning=FALSE}
codes <- c("NA", "ECOWAS","Other Africa", "China", "India", 
           "United States", "Europe", "Rest of World" )
x <- ggplot(data = sample_market, aes(x= market_1)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Market 1") +
  scale_x_continuous(breaks=seq(0,7,1), labels = codes) +
  scale_y_continuous(breaks = seq(0,50,5)) +
  theme_light() 
x
```

#### 2
```{r r Plot 4.1.2, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = sample_market, aes(x= market_2)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Market 2") +
  scale_x_continuous(breaks=seq(0,7,1), labels = codes) +
  scale_y_continuous(breaks = seq(0,50,5)) +
  theme_light() 
x
```

#### 3
```{r r Plot 4.1.3, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = sample_market, aes(x= market_3)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Market 3") +
  scale_x_continuous(breaks=seq(0,7,1), labels = codes) +
  scale_y_continuous(breaks = seq(0,50,5)) +
  theme_light() 
x
```

#### 4
```{r r Plot 4.1.4, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = sample_market, aes(x= market_4)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Market 4") +
  scale_x_continuous(breaks=seq(0,7,1), labels = codes) +
  scale_y_continuous(breaks = seq(0,50,5)) +
  theme_light() 
x
```

### c11: What are the THREE MOST IMPORTANT things you spend your business profit on? {.tabset}

```{r}
sample_important <- subset(data1, select = c(hid,c11a, c11b, c11c)) %>%
                  mutate(thing_1 = ifelse(is.na(c11a)==TRUE, 0, c11a),
                         thing_2 = ifelse(is.na(c11b)==TRUE, 0, c11b),
                         thing_3 = ifelse(is.na(c11c)==TRUE, 0, c11c))
```
0=NA, 1=Paying of children’s school fees, 2=Healthcare, 3=Upkeep of the home, i.e. food,
4=Re-investment in the business, 5=Invest in other business, 6=Savings (e.g. Bank/ Susu), 
7= Loans to workers, 8 = Non-wage benefits for your workers, 9=Other (Specify

#### 1
```{r r Plot 5.1, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = sample_important, aes(x= thing_1)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Thing 1") +
  scale_x_continuous(breaks=seq(1,9,1)) +
  scale_y_continuous(breaks = seq(0,650,50)) +
  theme_light() 
x
```

#### 2
```{r r Plot 5.2, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = sample_important, aes(x= thing_2)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Thing 2") +
  scale_x_continuous(breaks=seq(0,9,1)) +
  scale_y_continuous(breaks = seq(0,650,50)) +
  theme_light() 
x
```

#### 3
```{r r Plot 5.3, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = sample_important, aes(x= thing_3)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Thing 3") +
  scale_x_continuous(breaks=seq(0,9,1)) +
  scale_y_continuous(breaks = seq(0,650,50)) +
  theme_light() 
x
```

### Certificate {.tabset}
#### D8: Certification is a strategy used by some, but not all firms. 
```{r message=FALSE, warning=FALSE}
library(reshape2)
certi <- subset(ACE_G, select = c(hid, 421:432, 439))
certi <- certi %>% mutate_if(is.character, list(~na_if(.,"")))
certi_dummy <- certi %>%
  mutate(special = ifelse(is.na(d8a_11_sp)==TRUE, 2, 1)) %>%
  select(!c(d8a_11_sp, d9))
certi_melt <- melt(certi_dummy,  id.vars = 'hid', variable.name = 'certificate')
certi_melt <- na.omit(certi_melt)
certi_final <- certi_melt %>% 
    group_by(hid) %>% 
    summarise(value = min(value), .groups = 'drop')
certi_final <- distinct(certi_final)

```

```{r r Plot 6.1, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = certi_final, aes(x= value)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("Do you have a certificate?") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(breaks = seq(0,650,50)) +
  theme_light() 
x
```

#### D9:Does your firm have any certificate/code of conduct/agreement that is specific to your buyer?
```{r r Plot 6.2, results='asis', message=FALSE, warning=FALSE}
x <- ggplot(data = certi, aes(x= d9)) +
   geom_bar(fill="skyblue", color="black") +
  ylab("Observations") +
  xlab("") +
  scale_x_continuous(breaks=seq(1,2,1), labels = c("Yes", "No")) +
  scale_y_continuous(breaks = seq(0,650,50)) +
  theme_light() 
x
```

### Regression {.tabset}
```{r message=FALSE, warning=FALSE}
reg_sample <- subset(ACE_G, select = c(hid,a5b,b22_a,b22b_3, b2, b6,b8a, b25a,b25b,
                                       d6a, g1, c2a_1, c2a_2,c2a_3,c4,c7c, d9,
                                       238:240, b24c_3, b24d_3)) %>%
  mutate(outside = ifelse(b22b_3==3, 1, 0),
         outside_ghana = ifelse(is.na(outside)==TRUE, 0, outside)) %>%
  select(!c(b22b_3, outside))

reg_sample$b24c_3[is.na(reg_sample$b24c_3) == TRUE] <- 0
reg_sample$b24d_3[is.na(reg_sample$b24d_3) == TRUE] <- 0
# invest
re_invest <- subset(ACE_G, select = c(hid,c11a, c11b, c11c))
re_invest_melt <- melt(re_invest,  id.vars = 'hid', variable.name = 'thing')
re_invest_dummy <- re_invest_melt %>%
  mutate(value = ifelse(is.na(value)==TRUE, 0, value),
         re_invest = ifelse(value==4, 1, 0)) %>%
  select(c(hid, re_invest))
re_invest_dummy <- re_invest_dummy %>%
  group_by(hid) %>% 
  summarise_each(funs(max))

# help from buyers and suppliers
help <- subset(ACE_G, select = c(hid,199:205))
help_melt <- melt(help,  id.vars = 'hid', variable.name = 'help')
help_dummy <- help_melt %>%
  mutate(value = ifelse(is.na(value)==TRUE, 0, value),
         help = ifelse(value==0, 0, 1)) %>%
  select(c(hid, help))
help_dummy <- help_dummy %>%
  group_by(hid) %>% 
  summarise_each(funs(max))

# business improvements
improv <- subset(ACE_G, select = c(hid,183:190))
improv$b16i_sp[improv$b16i_sp ==""]<-NA
improv <- improv %>%
  mutate(b16i_sp = ifelse(is.na(b16i_sp)==TRUE, 2, 1))
improv_melt <- melt(improv,  id.vars = 'hid', variable.name = 'improv')
improv_dummy <- improv_melt %>%
  mutate(improv = ifelse(value==2, 0, 1)) %>%
  select(c(hid, improv))
improv_dummy <- improv_dummy %>%
  group_by(hid) %>% 
  summarise_each(funs(max))


reg_sample <- left_join(reg_sample, re_invest_dummy, by = "hid")
reg_sample <- left_join(reg_sample, help_dummy, by = "hid")
reg_sample <- left_join(reg_sample, improv_dummy, by = "hid")
reg_sample <- left_join(reg_sample, certi_final, by = "hid")
names(reg_sample)[names(reg_sample) == 'value'] <- "certification"

reg_sample <- reg_sample %>%
  mutate(certificate = ifelse(is.na(certification)==TRUE, 0, certification)) %>%
  select(!c(certification))

reg_df <- reg_sample %>%
  mutate(register = ifelse(b8a == 2, 0, b8a),
         long_term_s = ifelse(b25a == 2, 0, b25a),
         long_term_b = ifelse(b25b == 2, 0, b25b),
         foreign_part = ifelse(d6a == 2, 0, d6a),
         training = ifelse(g1 == 2, 0, g1),
         certi = ifelse(certificate==2, 0, certificate),
         certi_agree = ifelse(d9==2, 0, d9),
         end = ifelse(b22ii==2, 0, b22ii),
         intermediary = ifelse(b22iii==2,0, b22iii),
         intermediary_long = ifelse(b22iv == 2, 0, b22iv),
         end_outside_ghana = ifelse(b24c_3 ==3, 1, b24c_3),
         inter_outside_ghana = ifelse(b24d_3 == 3, 1, b24d_3),
         region = a5b,
         buyers_number = b22_a) %>%
  select(!c(b8a,b25a,b25b,d6a,g1,certificate, d9, b22ii,b22iii,b22iv, b24c_3,b24d_3,a5b,b22_a))
reg_df <- transform(reg_df, sector_a = substr(b2, 1, 1), sector_b = substr(b2, 2, 4))
reg_df <- na.omit(reg_df)
```

```{r message=FALSE, warning=FALSE}
reg1 <- lm(c4/1000 ~ b6 + register + long_term_s + long_term_b + 
             foreign_part + training + outside_ghana + help + end + intermediary +
             intermediary_long + end_outside_ghana + inter_outside_ghana + 
             factor(sector_a) +factor(region) + factor(buyers_number), data= reg_df)

reg2 <- lm(c7c/1000 ~ b6 + register + long_term_s + long_term_b + 
             foreign_part + training + outside_ghana + help+ end + intermediary +
             intermediary_long + end_outside_ghana + inter_outside_ghana + 
             factor(sector_a) +factor(region) + factor(buyers_number), data= reg_df)

reg3 <- lm(certi ~ b6 + register + long_term_s + long_term_b + 
             foreign_part + training + outside_ghana +help+end + intermediary +
             intermediary_long + end_outside_ghana + inter_outside_ghana + 
             factor(sector_a) +factor(region) + factor(buyers_number), data= reg_df)

reg4 <- lm(certi_agree ~ b6 + register + long_term_s + long_term_b + 
             foreign_part + training + outside_ghana +help+ end + intermediary +
             intermediary_long + end_outside_ghana + inter_outside_ghana + 
             factor(sector_a) +factor(region) + factor(buyers_number), data= reg_df)

reg5 <- lm(re_invest ~ b6 + register + long_term_s + long_term_b + 
             foreign_part + training + outside_ghana +help+ end + intermediary +
             intermediary_long + end_outside_ghana + inter_outside_ghana + 
             factor(sector_a) +factor(region) + factor(buyers_number), data= reg_df)

reg6 <- lm(improv ~ b6 + register + long_term_s + long_term_b + 
             foreign_part + training + outside_ghana + help+end + intermediary +
             intermediary_long + end_outside_ghana + inter_outside_ghana + 
             factor(sector_a) +factor(region) + factor(buyers_number), data= reg_df)
```


```{r message=FALSE, warning=FALSE, results='asis'}
stargazer(reg1,reg2, reg3,reg4,reg5,reg6, type="html", column.sep.width = "4pt",
          single.row = FALSE, font.size = "small",
          dep.var.labels = c("Porfit before Covid<br>/1000","Sales<br>/1000",
                             "Certificate<br>(dummy)", "Agreement of<br>Certificate(dummy)",                            "Re-investment<br>(dummy)","Improvment<br>(dummy)"),
          covariate.labels= c("Size(1-3)", "Registeration(0-1)", "Long-term with Suppliers(0-1)",
                              "Long-term with Buyers(0-1)", "Foreign Partners(0-1)",
                              "Training(0-1)", "Outside Ghana(0-1)","Help", 
                              "End-Customer(0-1)", "Intermediary(0-1)",
                              "Intermediary-long(0-1)","End-customer outside Ghana(0-1)",
                              "Intermediary outside Ghana(0-1)"),
          column.separate = c(1,1,1,1,1,1))
```
