---
title: "lesotho_test"
author: "Zixin"
date: "2022-11-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require("rgdal")) {install.packages("rgdal"); library("rgdal")}
if(!require("maptools")) {install.packages("maptools"); library("maptools")}
if(!require("sf")) {install.packages("sf"); library("sf")}
if(!require("dplyr")) {install.packages("dplyr"); library("dplyr")}
if(!require("tidyr")) {install.packages("tidyr"); library("tidyr")}
if(!require("broom")) {install.packages("broom"); library("broom")}
if(!require("readxl")) {install.packages("readxl"); library("readxl")}
if(!require("haven")) {install.packages("haven"); library("haven")}
if(!require("lfe")) {install.packages("lfe"); library("lfe")}
if(!require("lmtest")) {install.packages("lmtest"); library("lmtest")}
if(!require("sandwich")) {install.packages("sandwich"); library("sandwich")}
if(!require("stargazer")) {install.packages("stargazer"); library("stargazer")}
```

```{r message=FALSE, warning=FALSE}
#import excel sheet
diplomat <- read_xlsx("diplomats.xlsx")
diplomat_region <- diplomat %>%
  select(c(1,4,5,9:11)) %>%
  drop_na(region)

#merge aiddata with amount
lesotho_aiddata <- read_xlsx("lesotho_aiddata.xlsx")
aiddata_amount <- read_xlsx("aiddata_amount.xlsx") %>%
  select(c("project_id", "usd_current"))

lesotho_merge <- left_join(lesotho_aiddata, aiddata_amount, by = "project_id") 

lesotho_aiddata <- lesotho_merge %>%  
  drop_na(usd_current) %>%
  select(c(4,5,6,7,13,16,33,58)) 
names(lesotho_aiddata)[names(lesotho_aiddata) == 'year_'] <- 'year'

lesotho_aiddata_sum <- lesotho_aiddata %>%
  group_by(year) %>%
  summarise(usd_amount = sum(usd_current)) 

lesotho_aiddata_flow <- lesotho_aiddata %>%  
  group_by(year, flow_class) %>%
  summarise(usd_amount = sum(usd_current))

lesotho_aiddata$usd_amount <- ave(lesotho_aiddata$usd_current, lesotho_aiddata$year, FUN=sum)
```

```{r message=FALSE, warning=FALSE}
#import the shapefile
shape <- readOGR("gadm41_LSO_shp/gadm41_LSO_1.shp", stringsAsFactors=FALSE)
#par(mar=c(0,0,0,0))
#plot(shape,  col="skyblue", lwd=0.5 )

#get the longtitude and latitude from shape file
region.map <- tidy(shape, region = "NAME_1")
#get the mean of long and lat for each region
region_code <- region.map %>%
  group_by(id) %>%
  summarise(mean_long=mean(long),
            mean_lat= mean(lat))
names(region_code)[names(region_code) == 'id'] <- 'region'

#merge lat and long of two datasets
diplomat_merge_region <- left_join(diplomat_region, region_code, by = "region") %>%
  filter(year >= 2000 & year <= 2012) %>%
  mutate(dummy_region = ifelse(region == 'Maseru', 1, 0))

```

```{r message=FALSE, warning=FALSE}
#Run OLS regression to see the effect of a diplomatic visit on aid allocation to Lesotho 
#(so the aid allocation variable should be a year after the visits)
lesotho_aiddata_sum_lag <- lesotho_aiddata_sum
lesotho_aiddata_sum_lag$year <- lesotho_aiddata_sum_lag$year - 1

diplomat_merge <- left_join(diplomat_merge_region, lesotho_aiddata_sum, by = "year")
diplomat_merge_lag <- left_join(diplomat_merge_region, lesotho_aiddata_sum_lag, by = "year")

## add 1 to amount incase 0 in some years
diplomat_merge$usd_amount[is.na(diplomat_merge$usd_amount)] <- 0
diplomat_merge$usd_amount <- diplomat_merge$usd_amount + 1

## add 1 to amount incase 0 in some years for lag merge file
diplomat_merge_lag$usd_amount[is.na(diplomat_merge_lag$usd_amount)] <- 0
diplomat_merge_lag$usd_amount <- diplomat_merge_lag$usd_amount + 1

#create a new dataset to see the situation of aid allocation after a year 
diplomat_visit <- diplomat_merge_region 
diplomat_visit$num <- 1
diplomat_visit <- diplomat_visit %>%
  group_by(year) %>%
  summarise(num = sum(num)) 

diplomat_visit_merge <- left_join(lesotho_aiddata_sum_lag, diplomat_visit, by = "year")
```


```{r message=FALSE, warning=FALSE}
# export dta and csv file
write.csv(diplomat_merge, "diplomats.csv")



#write_dta(diplomat_merge, "diplomats.dta")

```


```{r message=FALSE, warning=FALSE}
reg1 <- lm(log(usd_amount) ~ dummy_region, 
                    data = diplomat_merge)
cov_1 <- vcovHC(reg1)
se_1 <- sqrt(diag(cov_1))

reg2 <- lm(log(usd_amount) ~ dummy_region, 
                    data = diplomat_merge_lag)
cov_2 <- vcovHC(reg2)
se_2 <- sqrt(diag(cov_2))
##fixed effect 
##reg2 <- felm(log(usd_amount) ~ dummy_region | year | 0 | year, diplomat_merge)

reg3 <- lm(log(usd_amount) ~ num, 
                    data = diplomat_visit_merge)
cov_3 <- vcovHC(reg3)
se_3 <- sqrt(diag(cov_3))

```

```{r  Table 1, results ='asis', message=FALSE, warning=FALSE}
stargazer(reg1, reg2,reg3, type="html",
          dep.var.labels = c(""),
          column.labels = c("Total Flow<br>(log)", "Lag Total Flow<br>(log)","Lag Total Flow<br>(log)"),
          covariate.labels= c("Birthregion(dummy)", "Number of Visits"),
          se=list(se_1,se_2, se_3), 
          column.separate = c(1,1,1),
          notes.align = "l",
          notes = "Robust standard errors are in parentheses.")
```

All of these three are simple OLS models. The first one is the relationship between log(aid) and dummy variable birthregion, both of them are from the same year. The second one the same as the first one, except the time of aid is one year after the time of diplomatic visits. The third one is the relationship bettween the log(aid) and the number of visits, the time of log(aid) is one year after of the year of the visits.

```{r message=FALSE, warning=FALSE}
#check the country with most number of aid projects
a <- read_xlsx("a.xlsx")
a <- a %>% group_by(ADM0_NAME) %>% 
     summarise(total_count=n(),
               .groups = 'drop')
```
It's United Republic of Tanzania
